\documentclass[10pt,a4paper]{article}

\usepackage[margin=0.65in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{parskip}
\pagenumbering{gobble}

% Formatting
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{6pt}{4pt}

\setlist[itemize]{leftmargin=*, itemsep=2pt}

\begin{document}

%====================
% HEADER
%====================
\begin{center}
    {\LARGE \textbf{Yash Datir}} \\
    Senior Software Engineer — Frontend \& Full Stack \\
    Bengaluru, India \quad | \quad
    +91-7990097420 \quad | \quad
    \href{mailto:yashdatir@gmail.com}{yashdatir@gmail.com} \\
    \href{https://www.linkedin.com/in/yash-datir}{linkedin.com/in/yash-datir} \quad | \quad
    \href{https://yashdatir.github.io/Yash-Datir/}{Portfolio}
\end{center}

%====================
% SUMMARY
%====================
\section*{Professional Summary}

Software Engineer with 5+ years of experience building scalable, high-performance web applications using React, TypeScript, and Node.js. Proven track record of delivering production-grade systems, improving performance, and driving frontend architecture decisions. Experienced in AWS, system design fundamentals, and cross-functional collaboration to ship user-centric products at scale.

%====================
% SKILLS
%====================
\section*{Technical Skills}

\textbf{Languages:} TypeScript, JavaScript, HTML, CSS, C++, SQL \\
\textbf{Frontend:} React.js, Next.js, Redux, Web Performance, Accessibility, Responsive UI \\
\textbf{Backend:} Node.js, Express.js, REST APIs, Serverless Architecture \\
\textbf{Cloud:} AWS (Lambda, S3), CI/CD, Microservices Basics \\
\textbf{Tools:} Git, Webpack, Electron.js, Agile, System Design Fundamentals \\
\textbf{Concepts:} Scalability, Performance Optimization, Clean Architecture, Design Patterns

%====================
% EXPERIENCE
%====================
\section*{Professional Experience}

\textbf{SmartQ} \hfill Bengaluru, India \\
\textit{Software Engineer} \hfill Jun 2022 – Present
\begin{itemize}
    \item Led frontend development for large-scale enterprise products using React and TypeScript.
    \item Improved application performance and load times through code optimization and architecture refinements.
    \item Collaborated with product, backend, and design teams to deliver scalable user-facing features.
    \item Built reusable UI components and design patterns adopted across teams.
    \item Contributed to system design discussions, improving reliability and maintainability.
\end{itemize}

\textbf{IntelliMedia Networks} \hfill Ahmedabad, India \\
\textit{Full Stack Developer} \hfill Apr 2021 – Jun 2022
\begin{itemize}
    \item Developed full-stack features using React, Node.js, and AWS services.
    \item Designed REST APIs and improved frontend-backend integration efficiency.
    \item Delivered production-ready features with focus on performance and usability.
\end{itemize}

\textbf{Xelpmoc Design \& Tech} \hfill Bengaluru, India \\
\textit{Full Stack Engineer} \hfill Jan 2020 – Apr 2021
\begin{itemize}
    \item Built scalable web applications and reusable frontend modules.
    \item Worked across the stack delivering UI, APIs, and deployment workflows.
\end{itemize}

\textbf{Early Career Experience}
\begin{itemize}
    \item Software Engineer — Ruby Infotech
    \item Software Engineer Intern — Indian Oil Corporation Limited
    \item Team Lead (Programming) — NTC Robocon
\end{itemize}

%====================
% PROJECT IMPACT
%====================
\section*{Key Impact \& Achievements}

\begin{itemize}
    \item Delivered multiple production-grade React applications used by enterprise users.
    \item Drove frontend architecture improvements and reusable component strategies.
    \item Contributed to performance optimization initiatives across applications.
    \item Expanded from frontend specialist to full-stack engineer with cloud exposure.
    \item Mentored peers and contributed to engineering best practices.
\end{itemize}

%====================
% EDUCATION
%====================
\section*{Education}

\textbf{B.E. in Computer Engineering} \\
Neotech Institute of Technology \hfill 2016 – 2020

%====================
% CERTIFICATIONS
%====================
\section*{Certifications}

Networking Administrator \\
CutShort Certified JavaScript (Advanced) \\
CutShort Certified HTML/CSS \\
Generative AI Tools

\end{document}
